### 2021-09-02 documentos/pce.tex
unh

\section{PCE Maps} % {{{
\subsection{Quantum channels}
Quantum channels comprehend the most general linear operations that a quantum system undergo independently of its past~\cite{zimansbook,cirac}. To introduce their construction and properties, first let us define several objects. We will denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as $\hilbert_d$. The set of bounded operators over a Hilbert space \hilbert will be written as $\mcB(\hilbert)$, the subset of density matrices as $\mcS(\hilbert)$, which is in turn a subset of the so called trace-class operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.

@@

A remarkable consequence of positivity 
\subsection{Single qubit case} % {{{
\label{sec:single:qubit}
\todo{David escribe una primera version y luego Carlos itera}
Let us discuss the single qubit case of \pce{} maps, they are defined by its action over Bloch vectors, providing that
\begin{equation}
\rho=\frac{\one +\vec r \cdot \vec \sigma}{2},
\end{equation}
then they are defined as follows
\begin{equation}
r_i \mapsto \tau_i r_i
\end{equation}
where $\tau_k$ is either $1$ or $0$. A direct evaluation of the

@@

The density matrix $\rho$ of a system of $N$ qubits can be written in Pauli
matrices basis as 
\begin{equation}\label{eq:N_qubits_rho}
	\rho =\frac{1}{2^N} 
            \sum_\valpha r_\valpha \sigma_\valpha,
            \quad r_{\vec0}=1,
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
	%r_{0,\ldots,0}=1,
\end{equation}
where $\vec \alpha$ denotes a multi index $\qty(\alpha_0,\ldots,\alpha_N)$ and
each $\alpha_i=0,1,2,3$, 
$\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
\sigma_{\alpha_N}$ is the tensor product of Pauli matrices, and 
$r_{\vec \alpha}$ is the coefficient corresponding to the expansion
of the density matrix in the complete orthonormal basis $\{ \sigma_{\vec
\alpha} \}$. %In the sum each of the $N$ components of $\valpha$, i.e.
%$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$. 
Notice that $\sigma_{\vec 0} = \openone$, and since both $\tr \rho=1$ and 
$\tr \sigma_\valpha=\delta_{\valpha,\vec 0}$, then $r_{\vec 0}=1$. 
We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
matrix of a system of qubits.

@@

Consider the linear operations that simply attenuate the Pauli components of 
a multiqubit system:
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\end{equation}
These operations have been studied in \cite{} \cpnote{davalos, dale aca un pequeño 
rollo relevante quiza de una o dos frases. También debemos tener un nombre pues lo de la diagonazliación 
funciona para eso y quizá también seran relevantes para la parte de decoherencia}.
For the linear operation to preserve the trace of the density matrix, we require that 
$\tau_{\vec 0}=1$. 
\cpnote{Tocará ajustar el texto de acuerdo a lo que ponga Davalos aca}
A Pauli component erasing (PCE) operation is a \cpnote{Pauli diagonal operation}
%  A linear operation 
% $\mcE$ 
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
It is worth noticing that not all PCE maps are quantum operations. For single 
qubits, if just one of the $\taus=0$, the complete positivity condition 
is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
in this article to determine with $\taus$ lead to a valid quantum map.

>>>>

\section{PCE Maps} 
\subsection{Quantum channels} % {{{
Quantum channels comprehend the most general linear operations that a quantum
system undergo independently of its past~\cite{zimansbook,cirac}. To introduce
their construction and properties, first let us define several objects. We will
denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as
$\hilbert_d$. The set of bounded operators over a Hilbert space \hilbert will
be written as $\mcB(\hilbert)$, the subset of density matrices as
$\mcS(\hilbert)$, which is in turn a subset of the so called trace-class
operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied
here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.

@@

A remarkable consequence of positivity

% }}}
\subsection{Single qubit case} % {{{
\label{sec:single:qubit}
\todo{David escribe una primera version y luego Carlos itera}
Let us discuss the single qubit case of \pce{} maps, they are defined by its action over Bloch vectors, providing that
\begin{equation}
\rho=\frac{\one +\vec r \cdot \vec \sigma}{2},
\end{equation}
then they are defined as follows
\begin{equation}
r_i \mapsto \tau_i r_i
\end{equation}
where $\tau_k$ is either $1$ or $0$. A direct evaluation of the

@@

The density matrix $\rho$ of a system of $N$ qubits can be written in Pauli
matrices basis as 
\begin{equation}\label{eq:N_qubits_rho}
	\rho =\frac{1}{2^N} 
            \sum_\valpha r_\valpha \sigma_\valpha,
%             \quad r_{\vec0}=1,
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
	%r_{0,\ldots,0}=1,
\end{equation}
where $\vec \alpha$ denotes a vector index $\qty(\alpha_0,\ldots,\alpha_N)$,
$\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
\sigma_{\alpha_N}$ is the tensor product of Pauli matrices, and 
$r_{\vec \alpha}$ is the coefficient corresponding to the expansion
of the density matrix in the complete orthonormal basis $\{ \sigma_{\vec
\alpha} \}$. In the sum each of the $N$ components of $\valpha$, i.e.
$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$\cpnote{Quizá se cambia
cuando hayamos escrito lo de un qubit}. 
Notice that $\sigma_{\vec 0} = \openone$, and since both $\tr \rho=1$ and 
$\tr \sigma_\valpha=\delta_{\valpha,\vec 0}$, then $r_{\vec 0}=1$. 
We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
matrix of a system of qubits.

@@

Consider the linear operations that simply attenuate the Pauli components of 
a multiqubit system:
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\end{equation}
These operations have been studied in \cite{} \cpnote{davalos, dale aca un pequeño 
rollo relevante quiza de una o dos frases. También debemos tener un nombre pues lo de la diagonazliación 
funciona para eso y quizá también seran relevantes para la parte de decoherencia}.
For the operation to preserve the trace of the density matrix, we require that 
$\tau_{\vec 0}=1$. 
\cpnote{Tocará ajustar el texto de acuerdo a lo que ponga Davalos aca}
A Pauli component erasing (PCE) operation is a \cpnote{Pauli diagonal operation}
%  A linear operation 
% $\mcE$ 
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
It is worth noticing that not all PCE maps are quantum operations. For single 
qubits, if just one of the $\taus=0$, the complete positivity condition 
is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
in this article to determine with $\taus$ lead to a valid quantum map.
